Fig1

### 2020-08-06 analysis/figure-1.Rmd
higher res?
remove unneded packages

```{r setup, include=FALSE}
library(tidyverse)
library(cowplot)
library(Rtsne)
library(kableExtra) 
library(ggtext) # for italic fonts

@@

```{r write}
pdf(file="../figures/fig1-1.pdf", width=7, height=4.5)
plot(fig1)
dev.off()
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(cowplot)
library(Rtsne)

@@

```{r write}
pdf(file="../figures/fig1-1.pdf", width=7, height=4.5)
plot(fig1)
dev.off()

png("../figures/fig1-1.png", width = 7, height = 4.5, 
    units = 'in', res = 300)
plot(fig1) # Make plot
dev.off()
```
